%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
% \input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

\usepackage{fontspec}

% Set the main font family to Geist
\setmainfont{Geist-Regular.otf}[
    ItalicFont = Geist-Light.otf, % Assuming you want Light for italic, or find a specific Italic file if available
    BoldFont = Geist-Bold.otf,
    BoldItalicFont = Geist-Medium.otf, % Assuming Medium for bold italic, adjust as needed
]


% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeadingLink}[3]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \small \href{#2}{\underline{#3}}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Tomáš Žifčák} \\ \vspace{4pt}
    \normalsize
    \href{https://zifcak.dev}{\underline{www.zifcak.dev}} \quad $|$ \quad
    \href{https://linkedin.com/in/tomaszifcak/}{\underline{linkedin.com/in/tomaszifcak}} \quad $|$ \quad
    \href{https://github.com/tomz197/}{\underline{github.com/tomz197}} \\ \vspace{2pt}
    \underline{tomas.zifcak197@gmail.com} \quad $|$ \quad
    \href{tel:+421944995915}{\underline{+421 944 995 915}} 
    \vspace{-8pt}
\end{center}

%------SUMMARY-------
\section{Summary}
Highly motivated developer with 3 years of proven experience in designing, developing, deploying, and maintaining web and mobile applications using React, Python, Next.js, Go, and React Native. 
    \vspace*{2.0\multicolsep}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Masaryk University}{Sep. 2023 -- June 2026 (Expected)}
      {Bachelor's degree in Computer Science}{Brno, Czech Republic}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading % For Full Stack Developer - Company name is CORA GEO, Job Title is Full Stack Developer
      {Full Stack Developer}{Aug 2023 -- Present} % Company Name, Dates
      {CORA GEO}{Poprad, Slovakia (Remote)} % Job Title, Location
      \resumeItemListStart
        \resumeItem{Key member of a small team that designed, developed, and launched a new web portal from scratch to production in under 5 months.}
        \resumeItem{Developed the full-stack application using Node.js for backend logic and Next.js for the user interface.}
        \resumeItem{Engaged in diverse set of development tasks, including UI/UX design, API creation, and PostgreSQL database architecture.}
        \resumeItem{Provided ongoing maintenance, bug fixes, and updates based on user feedback for the deployed applications.}
      \resumeItemListEnd

    \resumeSubheading % For Frontend Developer - Company name is CORA GEO, Job Title is Frontend Developer
      {Frontend Developer}{Jul 2022 -- Aug 2023} % Company Name, Dates
      {CORA GEO}{Poprad, Slovakia (Hybrid)} % Job Title, Location
      \resumeItemListStart
        \resumeItem{Led the successful rewrite of 3 legacy mobile applications to one React Native, resulting in less maintenance and notable improvements in performance and user experience.}
        \resumeItem{Streamlined mobile development by merging multiple applications into a single, unified React Native codebase.}
        \resumeItem{Designed and implemented new features and UI enhancements for the cross-platform mobile application.}
        \resumeItem{Mentored and onboarded 4 student interns, guiding them on best practices and project contributions.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeadingLink
          {\textbf{Bageta Express} $|$ \emph{Next.js, React, Typescript, SQLite, MySQL}}{https://bageta.express}{www.bageta.express}
          \resumeItemListStart
            \resumeItem{Developed a web application to streamline school lunch ordering for students and a local restaurant.}
            \resumeItem{Successfully presented the application to clients (school and restaurant), secured its adoption, and managed initial marketing efforts.}
            \resumeItem{Engineered the platform using Next.js and TypeScript, enabling users to browse menus and place orders.}
            \resumeItem{Iteratively developed features based on client feedback, ensuring high reliability for order management and reporting; currently serving active users.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeadingLink
          {\textbf{Course Recommender} $|$ \emph{Python, React, Content-Based Filtering, Google Cloud}}{https://muni.courses}{www.muni.courses}
          \resumeItemListStart
            \resumeItem{Co-developed a course recommendation system to help students discover relevant courses.}
            \resumeItem{Implemented a content-based filtering algorithms for personalized recommendations and built UI/UX.}
            \resumeItem{Deployed the application on Google Cloud Platform, establishing an automated CI/CD pipeline.}
            \resumeItem{Enabled tailored suggestions based on user-selected courses, enhancing course discovery.}
          \resumeItemListEnd 
          \vspace{-13pt}
      \resumeProjectHeadingLink
          {\textbf{OS Quiz Platform} $|$ \emph{React.js}}{https://os.zifcak.dev}{os.zifcak.dev}
          \resumeItemListStart
            \resumeItem{Created a popular OS quiz web application using React.js, attracting 400+ users (100 weekly active) by providing needed practice resources for university students.}
            \resumeItem{Designed an interactive and responsive UI to enhance the student learning experience.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeadingLink
          {\textbf{MongoDB Analyze Tool} $|$ \emph{Go, MongoDB}}{https://github.com/tomz197/mongodb-analyze}{github.com/tomz197/mongodb-analyze}
          \resumeItemListStart
            \resumeItem{Developed a command-line tool in Go to analyze MongoDB collections, detecting data types and inconsistencies to aid data structure understanding.}
            \resumeItem{Provided analysis results in both tabular and JSON formats for ease of use and integration.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, TypeScript, Python, Go, C\#, SQL, C, C++} \\
     \textbf{Frameworks \& Libraries}{: React, React Native, Node.js, Next.js, Express.js, NestJS} \\
     \textbf{Developer Tools \& Platforms}{: Git, GitHub, Gitlab, Docker, Kubernetes, Terraform, Google Cloud Platform} \\
     \textbf{Databases}{: PostgreSQL, SQLite, MongoDB, MySQL, } \\
     \textbf{Concepts}{: UI/UX Design, CI/CD, Machine Learning}
    }}
 \end{itemize}
 \vspace{-16pt}

%-----------INVOLVEMENT---------------
% Section removed as per request

\end{document}
